Autonomous Oceanographic Data Collection using Excursion Sets of Vector-valued Gaussian Random Fields

### 2020-06-22 main_new.tex
updates

We denote by $\gp$ a vector-valued random field indexed by some
arbitrary domain $\domain$, and assume values of the field at any
fixed location $\x \in \domain$, denoted $\gp[\x]$, to be a
$\no$-variate random vector ($\no\geq 2$). In the river plume
characterization case, $\domain$ is a prescribed domain in the fjord
of Trondheim (for the purpose of our AUV application, a discretization
of a $2$-dimensional domain at fixed depth is considered), and $\no=2$
with responses of temperature and salinity. A bivariate GRF model is
assumed for $\gp$. To motivate concepts,
Figure~\ref{example_excu}(left and middle) shows a realization of such
a vector-valued GRF on
$\domain=(0,1)^2$. Figure~\ref{example_excu}(right) represents a
by-product of interest derived from these realizations, namely regions
i) in red, where both temperature and salinity are high (i.e.,
exceeding respective thresholds), indicative of ocean water ii) in
white, where both temperature and salinity are low, indicative of
riverine water, and iii) in pink, where one variable is above and the
other below their respective thresholds, indicative of mixed waters.

\begin{figure}[h!] \centering
  \includegraphics[width=0.99\textwidth]{Figures/example_excu_1.png}
  \caption{Realization of a bivariate GRF and excursion set above some threshold ({\bf{JE: are means around 5 and 30 here, so same as later in the example?}} ). Joint excursion in red, excursion of a single variable in pink.}
\label{example_excu}
\end{figure}

@@

If we assume that $\gp$ has
continuous trajectories (almost surely) and $T$ is closed, then
$\es$ becomes a Random Closed Set
\citep{Molchanov2005} and concepts from the theory of random sets will prove useful in characterizing the distribution of the volume of $\es$ under some measure defined on the domain.
%\textcolor{red}{Is this really needed?} 
Note that while some aspects of the developed approaches do not call for a
specific form of $\T$, we will often stick for simplicity to the case
of orthants
($\T=(-\infty, t_1] \times \dots \times (-\infty, t_{\no}]$ where
$t_1,\dots, t_{\no} \in \R$) as this will allow efficient calculation
of several key quantities. Note that changing some $\leq$ inequalities
to $\geq$ ones would lead to immediate adaptations.

>>>>

We denote by $\gp$ a vector-valued random field indexed by some
arbitrary domain $\domain$, and assume values of the field at any
fixed location $\x \in \domain$, denoted $\gp[\x]$, to be a
$\no$-variate random vector ($\no\geq 2$). In the river plume
characterization case, $\domain$ is a prescribed domain in
Trondheimsfjord, Norway (for the purpose of our AUV application, a
discretization of a $2$-dimensional domain at fixed depth is
considered), and $\no=2$ with responses of temperature and salinity. A
bivariate GRF model is assumed for $\gp$. To motivate concepts,
Fig.~\ref{example_excu} (left and middle \kc{If you split this figure
  in its parts and add labels, it would be more elegant and precise to
  explicitly refer to them.}) shows a realization of such a
vector-valued GRF on $\domain=(0,1)^2$. Fig.~\ref{example_excu} (right
\kc{See above}) represents a by-product of interest derived from these
realizations, namely regions i) in red, where both temperature and
salinity are high (i.e., exceeding respective thresholds), indicative
of ocean water ii) in white, where both temperature and salinity are
low, indicative of riverine water, and iii) in pink, where one
variable is above and the other below their respective thresholds,
indicative of mixed waters.

\begin{figure}[h!] \centering
  \includegraphics[width=0.99\textwidth]{Figures/example_excu_1.png}
  \caption{Realization of a bivariate GRF and excursion set above some
    threshold ({\kc{JE: are means around 5 and 30 here, so same as
        later in the example?}} ). Joint excursion in red, excursion
    of a single variable in pink.}
\label{example_excu}
\end{figure}

@@

If we assume that $\gp$ has continuous trajectories (almost surely
\kc{This seems very handwavy; would delete}) and $T$ is closed, then
$\es$ becomes a Random Closed Set \citep{Molchanov2005} and concepts
from the theory of random sets will prove useful in characterizing the
distribution of the volume of $\es$ under some measure defined on the
domain.
%\textcolor{red}{Is this really needed?} 
Note that while some aspects of the developed approaches do not call for a
specific form of $\T$, we will often stick for simplicity to the case
of orthants
($\T=(-\infty, t_1] \times \dots \times (-\infty, t_{\no}]$ where
$t_1,\dots, t_{\no} \in \R$) as this will allow efficient calculation
of several key quantities. Note that changing some $\leq$ inequalities
to $\geq$ ones would lead to immediate adaptations.
